---
title: "Impact of weight and number of cylinder on miles per gallon (MPG)"
author: "Antonio Avella"
date: "September 5, 2018"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, echo = FALSE, 
                      message = FALSE, warning = FALSE)
```

## Introduction

- This project was created as part of the Developing Data Products course of the Coursera [Data Science Specialization](https://www.coursera.org/specializations/jhu-data-science).

- The goal of the project is to create a web page presentation using R Markdown that features a plot created with Plotly, and to host the resulting web page on either GitHub Pages, RPubs, or NeoCities.

Using the `mtcars` dataset, we  plot the relationship
of weight and number of cylinders to gas mileage (`mpg`) using plotly plots.

We plot weight (`wt`) vs. mileage (`mpg`) spatially along the x/y axes and  
visualize the number of cylinders (`cyl`) as colors. 

## Visualizing the Data

```{r plot, echo=FALSE}
library(plotly)
plot_ly(data = mtcars, x = ~wt, y = ~mpg, 
        color = ~as.factor(cyl), 
        type = "scatter", 
        mode = "markers" ) %>%
  layout(title = "Car Data")
```

## Notes

### Source code

- The R Markdown source code of this presentation can be found in [this GitHub repository](https://github.com/Hetman70/R-Markdown-Presentation-Plotly).